---
title: "Problem Set 7 by Defne Tekin"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(ggplot2)
library(dplyr)
library(babynames)
```

## Including Plots
```{r}
babynames_riley_casey <- babynames %>% 
filter(name == "Riley" | name == "Casey")
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}

 ggplot(data = babynames_riley_casey, mapping = aes(x = year, y= prop, color = sex)) +
  geom_line() +
  xlab("Year") +
  ylab("Proportion") +
  ggtitle("Comparison of Casey and Riley") +
  facet_wrap(~ name)



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
